Bias in Allocation of ABM Agents

### 2015-08-20 Rmd/agent-allocation-bias.Rmd
Renamed ABM file

---
title: "Districts for ABM"
author: "Lyndon Estes"
date: "June 26, 2015"
output: 
  html_document:
    highlight: tango
    theme: spacelab
    toc: yes 
    number_sections: true
---

@@

Selection of magisterial districts and associated landcover sets for use in ABM example.

>>>>

---
title: "Bias in Allocation of ABM Agents"
author: "Lyndon Estes"
date: "June 26, 2015"
output: 
  html_document:
    highlight: tango
    theme: spacelab
    toc: yes 
    number_sections: true
---

@@

Selection of magisterial districts and associated landcover sets for use in ABM example, and analysis of bias after initial allocation of agents performed based on available farmland estimated from 100 m downscaled versions of the landcover data.
